State of the Practice of Lattice Boltzmann Method Software Development

### 2021-07-27 StateOfPractice/Peter-Notes/Report/Report.tex
updated LBM report Abstract

We analyze the state of the practice of software development of Lattice Boltzmann Methods software domain by quantitatively and qualitatively measuring, and comparing, 23 software packages. A general methodology for assessing the state of the practice of software development in scientific computing software domains is presented. A domain analysis of the Lattice Boltzmann Methods software family is made, and candidate software packages are identified and curated. The packages are assessed to answer software development related research questions to understand how software quality is impacted by software development choices, including principles, processes, and tools. Software developers are interviewed to identify development pain points, and to identify how software quality is ensured. Quantitative data is used to rank the software packages using the Analytical Hierarchy Process. The packages Ludwig, ESPResSo, and Palabos are ranked as the top three packages. Each of them scored high in at least several of the individual qualities that were quantitatively measured. The ranking designations are compared with rankings from the software development community. Recommendations for improving software along quality metrics are made. These include providing a detailed user manual and tutorials, explicitly stating the limits of the software, using user-friendly software languages, considering a peer review process, communicating development and contribution information, and using continuous integration and project management tools. This knowledge can be used to guide future development of scientific computing software along quality attributes to reduce software quality failures.\\

@@

We analyzed the state of the practice of software development of Lattice Boltzmann Methods software domain by quantitatively and qualitatively measuring, and comparing, 23 software packages along quality attributes. The software qualities that were assessed in this report are listed in Section \ref{softwarequalities}. A methodology for assessing the state of the practice of software development in SCS domains was presented. Domain packages were assessed to answer the software development related research questions listed in Section \ref{purpose} to understand how software quality is impacted by software development choices, including principles, processes, and tools. Software developers were interviewed to identify development pain points, and to identify how software quality is ensured. Quantitative data was used to rank the software packages using the AHP. The ranking designations were compared with rankings from the software development community, and we found that many of our top 10 ranked packages are ranked highly by a domain expert. Recommendations for improving software along quality metrics were made, and highlights are presented in Section \ref{highlightedrecommendations} of this conclusion. The findings of this report can be used to guide future development of SCS, specifically along quality attributes, and to reduce software quality failures.

>>>>

We analyze the state of the practice of software development in the Lattice Boltzmann Methods software domain by quantitatively and qualitatively measuring and comparing 23 software packages. We present a general methodology for assessing the state of the practice of software development in scientific computing software domains. We present a domain analysis of the Lattice Boltzmann Methods software family, and identify candidate software packages. We assess these packages to answer software development related research questions to understand how software quality is impacted by software development choices, including principles, processes, and tools. We interview software developers to identify development pain points, and to identify how software quality is ensured. We use quantitative data to rank the software packages using the Analytical Hierarchy Process, and rank Ludwig, ESPResSo, and Palabos as the top three packages. Each of them score high in at least several of the individual qualities that we quantitatively measure. We compare these rankings with rankings from the software development community. We make recommendations, such as providing a detailed user manual and tutorials, explicitly stating the limits of the software, using user-friendly software languages, considering a peer review process, communicating development and contribution information, and using continuous integration and project management tools.\\

@@

We analyzed the state of the practice of software development in the Lattice Boltzmann Methods software domain by quantitatively and qualitatively measuring, and comparing, 23 software packages along quality attributes. The software qualities that were assessed in this report are listed in Section \ref{softwarequalities}. A methodology for assessing the state of the practice of software development in SCS domains was presented. Domain packages were assessed to answer the software development related research questions listed in Section \ref{purpose} to understand how software quality is impacted by software development choices, including principles, processes, and tools. Software developers were interviewed to identify development pain points, and to identify how software quality is ensured. Quantitative data was used to rank the software packages using the AHP. The ranking designations were compared with rankings from the software development community, and we found that many of our top 10 ranked packages are ranked highly by a domain expert. Recommendations for improving software along quality metrics were made, and highlights are presented in Section \ref{highlightedrecommendations} of this conclusion. The findings of this report can be used to guide future development of SCS, specifically along quality attributes, and to reduce software quality failures.
